\documentclass[a4paper,10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{calc}
\usepackage[numbers]{natbib}
\usepackage[dvips]{graphicx}
%\usepackage[active]{srcltx}
\usepackage{pstricks}
\usepackage{psfrag}
\usepackage{hyperref}


\setlength{\textwidth}{7.1in}
\setlength{\topmargin}{-1.2in}
\setlength{\textheight}{11in}
\setlength{\oddsidemargin}{(\paperwidth - \textwidth)/2-1in}
\setlength{\evensidemargin}{(\paperwidth - \textwidth)/2-1in}
%\setlength{\parindent}{0in}
\setlength{\parskip}{\baselineskip}

\pagestyle{empty}

%\address{Alexander Holyoake\\ Trinity College \\ Cambridge CB2 1TQ \\ ajh203@cam.ac.uk}

%\signature{Your signature}

\begin{document}

\begin{flushright}
Alexander Holyoake \\ 8 St. James Road \\ Shrewsbury SY2 5YH \\ ajholyoake@gmail.com
\end{flushright}

\begin{flushleft} 
Mike Coughlan \\ Chief Engineer \\ Williams F1 \\ Grove \\ Wantage \\ Oxfordshire \\ OX12 0DQ
\end{flushleft}

\begin{flushright}
12\textsuperscript{th} October 2012
\end{flushright}


\noindent Dear Mr. Coughlan, 

I have recently finished a Ph.D. at the University of Cambridge concerning the mathematical modelling of granular physics and I am currently seeking employment as an engineer within the F1 industry. While I appreciate that Williams are not currently advertising for a relevant position I would be most grateful if you could have a look over my CV to see if my experience and skills would be suited to a role within the team. 

My formal education has hereto focussed primarily on applied mathematics. My undergraduate and  masters degrees mainly concentrated on a very theoretical and rigorous treatment of fluid dynamics. My Ph.D. initially aimed to carry on in a similar fashion but instead I chose to pursue an experimental and numerical avenue for my research, introducing me to a more physical and engineering approach to understanding real-world problems.

Conducting postgraduate research has required me to approach multifaceted problems in a logical and structured manner, and has provided me with experience in communicating complex ideas to both technical and non-technical audiences. My Ph.D. had a heavy emphasis on designing and performing experiments, as well as using computers extensively to analyse large amounts of data and solve predictive models. I used MATLAB for the majority of my calculations, and took great pleasure in making my (and others') code run as quickly as possible: extensively employing techniques such as vectorisation, and using the C extensions (MEX) framework to write time critical routines. I believe that the experience I have gained in the last few years could be extremely useful in a time-pressured environment. 

During my Ph.D. I became heavily involved in the university's Formula Student team, where I was one of 5 group leaders and oversaw a large part of the engineering programme. As well as this, I simulated and designed the intake and exhaust package, writing some custom software to aid the simulation process.  I found the challenge of working in a high-pressure team environment incredibly exciting and rewarding, which led me to decide that I wanted to leave academia and pursue a competitive engineering career. Given Williams’ position as one of the biggest teams in F1, and the clear intent it has for the future, I believe it would be a fantastic opportunity to be part of the team as it builds on this year’s successes.

I have been an ardent Formula One fan for many years. As I worked through my university education, I quickly found that the engineering behind the cars started to interest me as much as, if not more than the races and the championships themselves. I would love the opportunity to combine my passion for the sport with my scientific background, and work in the competitive and challenging environment of such an innovative Formula 1 team. 

Given the nature of the work that constituted my Ph.D., I believe that a position that involves a substantial amount of coding whilst retaining a need to understand the underlying physical principles would be ideal. Vehicle Dynamics, Simulation and Aero tools are all positions that I think I could perform very well in.

Should you have a position that you feel would be suitable for me either now or in the future, I would be grateful if you would consider my CV, which I am attaching.
\\

\noindent
Yours sincerely,\\ 

Alexander Holyoake  

\end{document}


