\documentclass[a4paper,10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{calc}
\usepackage[numbers]{natbib}
\usepackage[dvips]{graphicx}
%\usepackage[active]{srcltx}
\usepackage{pstricks}
\usepackage{psfrag}
\usepackage{hyperref}


\setlength{\textwidth}{7.1in}
\setlength{\topmargin}{-1.2in}
\setlength{\textheight}{11in}
\setlength{\oddsidemargin}{(\paperwidth - \textwidth)/2-1in}
\setlength{\evensidemargin}{(\paperwidth - \textwidth)/2-1in}
%\setlength{\parindent}{0in}
\setlength{\parskip}{\baselineskip}
\newcommand{\sendfirst}{Ian}
\newcommand{\sendlast}{Goddard}
\newcommand{\sendtitle}{Mr.}
\newcommand{\sendto}{\sendfirst\ \sendlast}
\pagestyle{empty}

%\address{Alexander Holyoake\\ Trinity College \\ Cambridge CB2 1TQ \\ ajh203@cam.ac.uk}

%\signature{Your signature}

\begin{document}

\begin{flushright}
Alexander Holyoake, \\ 8 St. James Road, \\ Shrewsbury, \\ Shropshire. \\ SY2 5YH \\ ajholyoake@gmail.com
\end{flushright}

\begin{flushleft} 
\sendto, \\ Lotus F1 Team, \\ Whiteways Technical Centre, \\ Enstone, \\ Oxon. \\ OX7 4EE
\end{flushleft}

\begin{flushright}
30\textsuperscript{th} May 2012
\end{flushright}


\noindent Dear \sendtitle\ \sendlast,

I am writing to you to apply for the Vehicle Dynamics position of the Lotus F1 Team graduate scheme as advertised in an email sent to the University of Cambridge engineering department. I have recently finished my Ph.D. in non-Newtonian experimental fluid dynamics at the applied mathematics department at Cambridge. 

I have always had an urge to build and understand things physically but I was also fascinated by the rigour of mathematics, and it was the latter that led me to choose my degree studies. I soon found that  I gravitated towards applied mathematics and eventually chose a project for my Ph.D. which combined experimental and numerical studies. During my doctorate, the majority of my time was spent designing and performing physical experiments and writing software to collect, filter and analyse large amounts of data, as well as solving predictive models numerically. I found the varied nature of my project very rewarding as I completed the entire process of data collection, analysis and model development myself, and experienced first hand the accuracy of predictions that a combination of mathematics and engineering can give. Conducting postgraduate research has required me to approach multifaceted problems in a logical and structured manner, and provided me with experience in communicating complex ideas to both technical and non-technical audiences. However, with my passion for F1 leading me to get very heavily involved in the university's formula student team, I realised that I thrive when working as part of a team to strict deadlines, especially where there is an element of competition involved. It was immensely satisfying seeing research translated into a physical object that was actually used to good effect. I strongly feel that working on cutting edge mathematical and physical problems at Lotus F1 would encompass the best aspects of both my Ph.D. and formula student experiences.

I have used MATLAB for the majority of the software produced in my Ph.D. and I take great pleasure in improving the performance of my (and others') code by extensively employing techniques such as vectorization, and using the C extensions (MEX) framework to write time critical routines. I have also developed data acquisition software in C++ and C. I believe that the experience I have gained in this area over the last few years could be extremely useful in a competitive environment where MATLAB in particular is used. I would love the chance to apply my knowledge and develop my skills further in a championship winning team that is well known to have a good working environment with great technical innovation. Lotus's performance so far this year, along with the new driver in-the-loop simulator, makes this a particularly exciting time for an engineer aspiring to a career in Formula 1 to be joining the team. 

In summary, I feel that I have the necessary skills and ambition for this position as a result of my programming and mathematical background as well as my motorsport experience through formula student. I would cherish the opportunity to contribute to an environment packed with driven, intelligent individuals, and to see the results of the team's work being just that bit better than everyone else's.

I am available for an interview at any time apart from the 25\textsuperscript{th} to the 28\textsuperscript{th} of June.

\noindent
Yours sincerely,\\ 

Alexander Holyoake   

\end{document}


